Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-11-02 manuscript/manuscript.tex
Edited Summary and Keywords

\begin{summary}
Summary of this paper 
\end{summary}

\begin{keywords}
Satellite gravity??, Numerical modelling, Structure of the Earth, Gravity anomalies and Earth structure, Numerical approximations and analysis, spatial analysis??
\end{keywords}

>>>>

\begin{summary}
We present a new open-soruce software that allows to compute the gravitational fields generated by any tesseroid whose density varies arbitrarily in depth, i.e. a forward gravity model in spherical coordinates for varying densities on the radial direction.
It is written in Python and Cython language and is compatible with the classes and functions of the library for geophysical modelling Fatiando a Terra.
It numerically approximates the gravitational fields by applying the Gauss-Legendre Quadrature along with a preexisting adaptive discretization algorithm and a new density-based discretization algorithm that control both the accuracy and the computation time of the forward model.
The first one is controlled by a predefined distance-size ratio ($D$) and reduces the errors due to the distance between the tesseroid and the computation point.
While the second one, regulated by a delta ratio ($\delta$), decreases the errors introduced by the variation of the density function.
We have also obtained analytical solutions for a spherical shell with variable density and compared them with the results of the numerical model in case of a linear, an exponential and a discontinuous density function.
These comparisons allowed to obtain default values for the distance-size and the delta ratio in order to guarantee the accuracy of the forward model.
The resulting optimal values of $D$ for the gravity potential, the components of its gradient and the Marussi tensor components are 1, 2 and 8, respectively.
While a $\delta=0.2$ is needed even for high varying exponential densities and discontinuous functions.
We have finally tested the new software by modelling the Neuquen sedimentary basin, located to the east of the Andes between 32$^\circ$S and 40$^\circ$S latitude, assigning a linear density variation to it and computing all the gravity fields it generates.
\end{summary}

\begin{keywords}
Numerical modelling, Numerical approximations and analysis, Gravity anomalies and Earth structure, Satellite gravity
\end{keywords}
